The UCD CASL SenseTile System

### 2009-06-29 papers/ModelBasedTestCaseGenerationDataStreamProtocol/paper.tex
an abstract of the abstract

@@

An abstract.

>>>>

OBJECTIVE: 
Specifications used as a blueprint for system development.
Specifications to generate test suite to validate the developed system.
Specifications to validate simulator of the developed system.
Apply to data stream processing: verify the stream is parsed correctly, 
verify the parsed stream output stream can be simulated.

METHODS: 
JML model.
JML tools to generate JUnit test suite.
JUnit test suite applied to developed system, to verify its correctness.
Junit test suite applied to simulator, to verify its correctness.

RESULTS: 
Proof developed system same behaviour as simulator.
Proof developed system and simulator verify the specifications.

CONCLUSIONS:
Specifications serves two purposes, and indirectly a third one.

@@
